---
title: "Sexual Scripts Master Thesis Visualizations & Diagnostics"
author: "Fanny Habacht"
date: "2023-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This code includes preparing the dataset further for the main analysis (total scores, removing non-hetero participants and nb/prefer not to say people, only extracting scales), as well as visualizations of the sexual script scales and diagnostics, such as multivariate normality and outliers.


# Packages
```{r}

packages <- c('tidyr', 'readr', 'dplyr', 'ggplot2', 'MVN', 'psych', 'cowplot', 'naniar', 'misty', 'missMethods')

lapply(packages, library, character.only = TRUE)

```


# Data
```{r}

data_clean <- read_csv('data_sexualscript_clean.csv') # load clean data

```


## Recoding reverse-coded items
```{r}

# only the Sakaluk et al scale has reverse-coded items

reverse_cols = c('player_3', 'player_4', 'emotionalsex_3')

data_clean[ , reverse_cols] = 7 - data_clean[ , reverse_cols]

```


## Removing participants not hetero and not male/female
```{r}

hetero <- 1
nonbinary <- 3
notsaid <- 4

# only non-binary participants
data_nonbinary <- data_clean %>% 
  filter(gender == nonbinary)


# only hetero and male/female
data_nothetero <- data_clean %>% 
  filter(sexuality != hetero) # only not hetero

data_onlyhetero <- data_clean %>%
  anti_join(data_nothetero)

data_notmaleorfemale <- data_onlyhetero %>% 
  filter(gender == nonbinary | gender == notsaid) # only male/female

data_onlyhetero_malefemale <- data_onlyhetero %>% 
  anti_join(data_notmaleorfemale)

```


## Extract only scales (remove demographics)
```{r}

data_heteroscales_raw <- data_onlyhetero_malefemale %>% 
  select(
    'id', 
    starts_with('sexualstandards'), 
    starts_with('complexity'), 
    starts_with('sexdrive'), 
    starts_with('performanceandorgasm'), 
    starts_with('player'), 
    starts_with('emotionalsex'), 
    starts_with('courtship'), 
    starts_with('initiators'), 
    starts_with('appearance'), 
    starts_with('doublestandards'), 
    starts_with('ammsa'), 
    starts_with('arranged'), 
    starts_with('situation'), 
    starts_with('sex'), 
    starts_with('sexlocation'), 
    starts_with('contraception'), 
    'metbefore', 
    'knownbefore',
    starts_with('substances'), 
    starts_with('drunkstoned'), 
    starts_with('consent'), 
    starts_with('afterfeeling'), 
    starts_with('outlook')) 

```


## Missing data screening and imputation
```{r}

# sum of missings

is.na(data_heteroscales_raw) %>%
  sum()


# location of missing values for each column

sapply(data_heteroscales_raw, function(x) which(is.na(x)))


# Little's MCAR test

na.test(data_heteroscales_raw, output = TRUE)


# EM imputation

set.seed(9191)

data_heteroscales <- impute_EM(data_heteroscales_raw,
                            stochastic = FALSE
                            )

```


# Creating total scores
```{r}

data_heteroscales <- data_heteroscales %>% 
  mutate(
    ammsa_total = rowMeans(
      select(data_heteroscales, starts_with('ammsa')),
      na.rm = FALSE),
    sakaluk_total = rowMeans(
      select(data_heteroscales,
             starts_with('sexualstandards'),
             starts_with('complexity'),
             starts_with('sexdrive'),
             starts_with('performanceandorgasm'),
             starts_with('player'),
             starts_with('emotionalsex')),
        na.rm = FALSE), 
    sakaluk_sexualstandards = rowMeans(
      select(data_heteroscales, starts_with('sexualstandards')),
      na.rm = FALSE),
    sakaluk_complexity = rowMeans(
      select(data_heteroscales, starts_with('complexity')),
      na.rm = FALSE),
    sakaluk_sexdrive = rowMeans(
      select(data_heteroscales, starts_with('sexdrive')),
      na.rm = FALSE),
    sakaluk_performanceorgasm = rowMeans(
      select(data_heteroscales, starts_with('performanceandorgasm')),
      na.rm = FALSE),
    sakaluk_player = rowMeans(
      select(data_heteroscales, starts_with('player')),
      na.rm = FALSE),
    sakaluk_emotionalsex = rowMeans(
      select(data_heteroscales, starts_with('emotionalsex')),
      na.rm = FALSE),
    seabrook_total = rowMeans(
      select(data_heteroscales,
             starts_with('courtship'), 
             starts_with('initiators'), 
             starts_with('appearance'), 
             starts_with('doublestandards')),
      na.rm = FALSE),
    seabrook_courtship = rowMeans(
      select(data_heteroscales, starts_with('courtship')),
      na.rm = FALSE),
    seabrook_initiators = rowMeans(
      select(data_heteroscales, starts_with('initiators')),
      na.rm = FALSE),
    seabrook_appearance = rowMeans(
      select(data_heteroscales, starts_with('appearance')),
      na.rm = FALSE),
    seabrook_doublestandards = rowMeans(
      select(data_heteroscales, starts_with('doublestandards')),
      na.rm = FALSE),
  )

```


# Saving datasets
```{r}

# dataset only scales hetero male/female
write.csv(data_heteroscales, 'data_sexualscript_heteroscales.csv', row.names = FALSE)

# dataset hetero male/female
write.csv(data_onlyhetero_malefemale, 'data_sexualscript_hetero_malefemale.csv', row.names = FALSE)

# dataset only nonbinary
write.csv(data_nonbinary, 'data_sexualscript_nonbinary.csv', row.names = FALSE)

```


# Visualizations hetero male/female

## Histograms

### AMMSA-21 total
```{r}

hist_ammsa <- 
  ggplot(data_heteroscales,
         aes(
           x = ammsa_total
         )) +
  geom_histogram(
    binwidth = .25,
    color = 'black',
    fill = 'grey'
  ) +
  scale_x_continuous(
    limits = c(1, 7),
    breaks = 1:7
  ) +
  labs(
    x = 'AMMSA Total',
    y = 'Frequency',
    title = 'AMMSA-21 (Bohner et al., 2022)'
  ) +
  theme_classic()

hist_ammsa

```


### Sakaluk

#### Sakaluk total
```{r}

hist_sakaluktotal <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_total
         )) +
  geom_histogram(
    binwidth = .25,
    color = 'black',
    fill = 'grey'
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Sexual Scripts Total',
    y = 'Frequency',
    title = 'Sexual Scripts Total (Sakaluk et al., 2014)'
  ) +
  theme_classic()

hist_sakaluktotal

```


#### Sakaluk sexual standards
```{r}

hist_sakaluksexualstandards <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_sexualstandards
         )) +
  geom_histogram(
    binwidth = .25,
    color = 'black',
    fill = 'grey'
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Sexual Standards',
    y = 'Frequency',
    title = 'Sexual Standards (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakaluksexualstandards

```


#### Sakaluk complexity
```{r}

hist_sakalukcomplexity <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_complexity
         )) +
  geom_histogram(
    binwidth = .25,
    color = 'black',
    fill = 'grey'
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Simplicity',
    y = 'Frequency',
    title = 'Sexual Simplicity/Complexity (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakalukcomplexity

```


#### Sakaluk sex drive
```{r}

hist_sakaluksexdrive <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_sexdrive
         )) +
  geom_histogram(
    binwidth = .25,
    color = 'black',
    fill = 'grey'
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Sex Drive',
    y = 'Frequency',
    title = 'Sex Drive (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakaluksexdrive

```


#### Sakaluk performance and orgasm
```{r}

hist_sakalukperformance <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_performanceorgasm
         )) +
  geom_histogram(
    binwidth = .25,
    color = 'black',
    fill = 'grey'
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Performance and Orgasm',
    y = 'Frequency',
    title = 'Performance and Orgasm (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakalukperformance

```


#### Sakaluk player
```{r}

hist_sakalukplayer <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_player
         )) +
  geom_histogram(
    binwidth = .25,
    color = 'black',
    fill = 'grey'
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Player',
    y = 'Frequency',
    title = 'Player (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakalukplayer

```


#### Sakaluk emotional sex
```{r}

hist_sakalukemotionalsex <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_emotionalsex
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Emotional Sex',
    y = 'Frequency',
    title = 'Emotional Sex (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakalukemotionalsex

```


#### Sakaluk histogram grid
```{r}

histgrid_sakaluk <- plot_grid(hist_sakaluksexualstandards, hist_sakalukcomplexity, hist_sakaluksexdrive, hist_sakalukperformance, hist_sakalukplayer, hist_sakalukemotionalsex, nrow = 3)

histgrid_sakaluk

```


### Seabrook

#### Seabrook total
```{r}

hist_seabrooktotal <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_total
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Total',
    y = 'Frequency',
    title = 'Sexual Scripts (Seabrook et al., 2016)'
  ) +
  theme_classic()

hist_seabrooktotal

```


#### Seabrook courtship
```{r}

hist_seabrookcourtship <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_courtship
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Courtship',
    y = 'Frequency',
    title = 'Courtship and Commitment (Seabrook et al., 2016)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_seabrookcourtship

```


#### Seabrook initiators
```{r}

hist_seabrookinitiators <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_initiators
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Initiators',
    y = 'Frequency',
    title = 'Men as initiators (Seabrook et al., 2016)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_seabrookinitiators

```


#### Seabrook appearance
```{r}

hist_seabrookappearance <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_appearance
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Appearance',
    y = 'Frequency',
    title = 'Women`s appearance (Seabrook et al., 2016)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_seabrookappearance

```


#### Seabrook double standards
```{r}

hist_seabrookdoublestandards <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_doublestandards
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 20, 30, 40, 50)
  ) +
  labs(
    x = 'Double Standards',
    y = 'Frequency',
    title = 'Double Standards (Seabrook et al., 2016)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_seabrookdoublestandards

```


#### Seabrook histogram grid
```{r}

histgrid_seabrook <- plot_grid(hist_seabrookcourtship, hist_seabrookinitiators, hist_seabrookappearance, hist_seabrookdoublestandards, nrow = 2)

histgrid_seabrook

```


### Krahé

#### Histogram grid items
```{r}

krahe_scale <- data_heteroscales %>%
  select(
    starts_with("arranged"),
    starts_with("situation"),
    starts_with("sex_"),
    starts_with("sexlocation"),
    starts_with("contraception"),
    starts_with("metbefore"),
    starts_with("knownbefore"),
    starts_with("substances"),
    starts_with("drunkstoned"),
    starts_with("consentboy"),
    starts_with("consentgirl"),
    starts_with("afterfeeling"),
    starts_with("outlook")
  )
    

krahe_scale %>% 
  pivot_longer(
        cols = everything(),
        names_to = "item",
        values_to = "value"
        ) %>% 
  ggplot(.,
         aes(
           x = value
         )) +
  facet_wrap(
    ~ item,
    nrow = 5) +
  geom_histogram(
    binwidth = 0.25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c (1, 5),
    breaks = 1:5
  ) +
  scale_y_continuous(
    limits = c(0,50),
    breaks = c(10, 30, 50)
  ) +
  labs(
    x = 'Value',
    y = 'Frequency',
    title = 'Sexual Scripts (Krahé et al., 2007)'
  ) +
  theme_classic(
    base_size = 9.5
  )

```


# Diagnostics (Normality, Outliers)

## Ammsa total
```{r}

ammsa_scale <- data_onlyhetero_malefemale %>% 
  select(starts_with('ammsa'))
  

# Normality and Outliers

diagnostics_ammsa <- mvn(ammsa_scale,
                         mvnTest = 'mardia',
                         multivariateOutlierMethod = 'adj', # adjusted quantile method
                         univariateTest = 'SW', # univariate normality Shapiro-Wilk
                         univariatePlot = 'box', # boxplot univariate outliers
                         showOutliers = TRUE, # multivariate outliers based on mahalanobis
                         showNewData = TRUE) # data without outliers

diagnostics_ammsa$univariateNormality # Shapiro-Wilk test

diagnostics_ammsa$Descriptives # univariate skewness and kurtosis

diagnostics_ammsa$multivariateNormality # mvn, skewness and kurtosis


# qqplot

ggplot(data_heteroscales,
        aes(
          sample = ammsa_total
        )) +
geom_qq(
  distribution = qnorm
) +
geom_qq_line(
  distribution = qnorm
) +
theme_classic()


# squared mahalanobis distances

cov_ammsa <- cov(ammsa_scale) # cov matrix

colmeans_ammsa <- colMeans(ammsa_scale)

mahal_ammsa <- mahalanobis(ammsa_scale, center = colmeans_ammsa, cov = cov_ammsa)

mahal_p_ammsa <- pchisq(mahal_ammsa, df = ncol(ammsa_scale), lower.tail = FALSE)

ID_ammsa <- 1:nrow(ammsa_scale)

mahal_data_ammsa <- data.frame(ID_ammsa, mahal_ammsa, mahal_p_ammsa)

arrange(mahal_data_ammsa, by = desc(mahal_ammsa))


```


## Sakaluk total
```{r}

sakaluk_scale <- data_onlyhetero_malefemale %>% 
  select(
    starts_with('sexualstandards'), 
    starts_with('complexity'), 
    starts_with('sexdrive'), 
    starts_with('performanceandorgasm'), 
    starts_with('player'), 
    starts_with('emotionalsex')
  )


# Normality and Outliers

diagnostics_sakaluk <- mvn(sakaluk_scale,
                           mvnTest = 'mardia',
                           multivariateOutlierMethod = 'adj',
                           univariateTest = 'SW',
                           univariatePlot = 'box',
                           showOutliers = TRUE,
                           showNewData = TRUE)


diagnostics_sakaluk$univariateNormality # Shapiro-Wilk test

diagnostics_sakaluk$Descriptives # univariate skewness and kurtosis

diagnostics_sakaluk$multivariateNormality # mvn, skewness and kurtosis


# qqplot

ggplot(data_heteroscales,
        aes(
          sample = sakaluk_total
        )) +
geom_qq(
  distribution = qnorm
) +
geom_qq_line(
  distribution = qnorm
) +
theme_classic()


# squared mahalanobis distances

cov_sakaluktotal <- cov(sakaluk_scale) # cov matrix

colmeans_sakaluktotal <- colMeans(sakaluk_scale)

mahal_sakaluktotal <- mahalanobis(sakaluk_scale, center = colmeans_sakaluktotal, cov = cov_sakaluktotal)

mahal_p_sakaluktotal <- pchisq(mahal_sakaluktotal, df = ncol(sakaluk_scale), lower.tail = FALSE)

ID_sakaluktotal <- 1:nrow(sakaluk_scale)

mahal_data_sakaluktotal <- data.frame(ID_sakaluktotal, mahal_sakaluktotal, mahal_p_sakaluktotal)

arrange(mahal_data_sakaluktotal, by = desc(mahal_sakaluktotal)) # arrange descending


```


## Seabrook total
```{r}

seabrook_scale <- data_onlyhetero_malefemale %>% 
  select(
    starts_with('courtship'), 
    starts_with('initiators'), 
    starts_with('appearance'), 
    starts_with('doublestandards')
  )


# Normality and Outliers

diagnostics_seabrook <- mvn(seabrook_scale,
                           mvnTest = 'mardia',
                           multivariateOutlierMethod = 'adj',
                           univariateTest = 'SW',
                           univariatePlot = 'box',
                           showOutliers = TRUE,
                           showNewData = TRUE)



diagnostics_seabrook$univariateNormality # Shapiro-Wilk test

diagnostics_seabrook$Descriptives # univariate skewness and kurtosis

diagnostics_seabrook$multivariateNormality # mvn, skewness and kurtosis


# qqplot

ggplot(data_heteroscales,
        aes(
          sample = seabrook_total
        )) +
geom_qq(
  distribution = qnorm
) +
geom_qq_line(
  distribution = qnorm
) +
theme_classic()


# squared mahalanobis distances

cov_seabrooktotal <- cov(seabrook_scale) # cov matrix

colmeans_seabrooktotal <- colMeans(seabrook_scale)

mahal_seabrooktotal <- mahalanobis(seabrook_scale, center = colmeans_seabrooktotal, cov = cov_seabrooktotal)

mahal_p_seabrooktotal <- pchisq(mahal_seabrooktotal, df = ncol(seabrook_scale), lower.tail = FALSE)

ID_seabrooktotal <- 1:nrow(seabrook_scale)

mahal_data_seabrooktotal <- data.frame(ID_seabrooktotal, mahal_seabrooktotal, mahal_p_seabrooktotal)

arrange(mahal_data_seabrooktotal, by = desc(mahal_seabrooktotal))


```


##########################################################################################


