---
title: "sexualscripts_thesis_visualizations_diagnostics"
author: "Fanny Habacht"
date: "2023-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This code includes preparing the dataset further for the main analysis (total scores, removing non-hetero participants and nb/prefer not to say people, only extracting scales), as well as visualizations of the sexual script scales and diagnostics, such as multivariate normality and outliers.


# Packages
```{r}

packages <- c('readr', 'dplyr', 'ggplot2', 'MVN', 'psych', 'cowplot')

lapply(packages, library, character.only = TRUE)

```


# Data
```{r}

data_clean <- read_csv('data_sexualscript_clean.csv') # load clean data

```


## Recoding reverse-coded items
```{r}

# only the Sakaluk et al scale has reverse-coded items

reverse_cols = c('player_3', 'player_4', 'emotionalsex_3')

data_clean[ , reverse_cols] = 7 - data_clean[ , reverse_cols]

```


## Removing participants not hetero and not male/female
```{r}

HETERO <- 1
NONBINARY <- 3
NOTSAID <- 4


data_nothetero <- data_clean %>% 
  filter(sexuality != HETERO)

data_onlyhetero <- data_clean %>% 
  anti_join(data_nothetero)


data_nonbinary <- data_clean %>% 
  filter(gender == NONBINARY)


data_notmaleorfemale <- data_onlyhetero %>% 
  filter(gender == NONBINARY | gender == NOTSAID)

data_onlyhetero_malefemale <- data_onlyhetero %>% 
  anti_join(data_notmaleorfemale)

```


## Extract only scales (remove demographics)
```{r}

data_heteroscales <- data_onlyhetero_malefemale %>% 
  select(9:123)

```


## Missing data screening
```{r}

is.na(data_heteroscales) %>% # sum of missings
  sum()


sapply(data_heteroscales, function(x) which(is.na(x))) # location of missing values for each column

```


# Creating total scores
```{r}

data_heteroscales <- data_heteroscales %>% 
  mutate(
    ammsa_total = rowMeans(
      select(data_heteroscales, starts_with('ammsa')),
      na.rm = F),
    sakaluk_total = rowMeans(
      select(data_heteroscales, 1:32),
      na.rm = F), 
    sakaluk_sexualstandards = rowMeans(
      select(data_heteroscales, starts_with('sexualstandards')),
      na.rm = F),
    sakaluk_complexity = rowMeans(
      select(data_heteroscales, starts_with('complexity')),
      na.rm = F),
    sakaluk_sexdrive = rowMeans(
      select(data_heteroscales, starts_with('sexdrive')),
      na.rm = F),
    sakaluk_performanceorgasm = rowMeans(
      select(data_heteroscales, starts_with('performanceandorgasm')),
      na.rm = F),
    sakaluk_player = rowMeans(
      select(data_heteroscales, starts_with('player')),
      na.rm = F),
    sakaluk_emotionalsex = rowMeans(
      select(data_heteroscales, starts_with('emotionalsex')),
      na.rm = F),
    seabrook_total = rowMeans(
      select(data_heteroscales, 33:54),
      na.rm = F),
    seabrook_courtship = rowMeans(
      select(data_heteroscales, starts_with('courtship')),
      na.rm = F),
    seabrook_initiators = rowMeans(
      select(data_heteroscales, starts_with('initiators')),
      na.rm = F),
    seabrook_appearance = rowMeans(
      select(data_heteroscales, starts_with('appearance')),
      na.rm = F),
    seabrook_doublestandards = rowMeans(
      select(data_heteroscales, starts_with('doublestandards')),
      na.rm = F),
  )

```


# Saving datasets
```{r}

# dataset only scales hetero male/female
write.csv(data_heteroscales, 'data_sexualscript_heteroscales.csv', row.names = F)

# dataset hetero male/female
write.csv(data_onlyhetero_malefemale, 'data_sexualscript_hetero_malefemale.csv', row.names = F)

# dataset only nonbinary
write.csv(data_nonbinary, 'data_sexualscript_nonbinary.csv', row.names = F)

```


# Visualizations hetero male/female

## Histograms

### AMMSA-21 total
```{r}

hist_ammsa <- 
  ggplot(data_heteroscales,
         aes(
           x = ammsa_total
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 7),
    breaks = 1:7
  ) +
  labs(
    x = 'AMMSA Total',
    y = 'Frequency',
    title = 'AMMSA-21 (Bohner et al., 2022)'
  ) +
  theme_classic()

hist_ammsa

```


### Sakaluk

#### Sakaluk total
```{r}

hist_sakaluktotal <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_total
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Sexual Scripts Total',
    y = 'Frequency',
    title = 'Sexual Scripts Total (Sakaluk et al., 2014)'
  ) +
  theme_classic()

hist_sakaluktotal

```


#### Sakaluk sexual standards
```{r}

hist_sakaluksexualstandards <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_sexualstandards
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Sexual Standards',
    y = 'Frequency',
    title = 'Sexual Standards (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakaluksexualstandards

```


#### Sakaluk complexity
```{r}

hist_sakalukcomplexity <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_complexity
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Simplicity',
    y = 'Frequency',
    title = 'Sexual Simplicity/Complexity (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakalukcomplexity

```


#### Sakaluk sex drive
```{r}

hist_sakaluksexdrive <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_sexdrive
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Sex Drive',
    y = 'Frequency',
    title = 'Sex Drive (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakaluksexdrive

```


#### Sakaluk performance and orgasm
```{r}

hist_sakalukperformance <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_performanceorgasm
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Performance and Orgasm',
    y = 'Frequency',
    title = 'Performance and Orgasm (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakalukperformance

```


#### Sakaluk player
```{r}

hist_sakalukplayer <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_player
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Player',
    y = 'Frequency',
    title = 'Player (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakalukplayer

```


#### Sakaluk emotional sex
```{r}

hist_sakalukemotionalsex <- 
  ggplot(data_heteroscales,
         aes(
           x = sakaluk_emotionalsex
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Emotional Sex',
    y = 'Frequency',
    title = 'Emotional Sex (Sakaluk et al., 2014)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_sakalukemotionalsex

```


#### Sakaluk histogram grid
```{r}

histgrid_sakaluk <- plot_grid(hist_sakaluksexualstandards, hist_sakalukcomplexity, hist_sakaluksexdrive, hist_sakalukperformance, hist_sakalukplayer, hist_sakalukemotionalsex, nrow = 3)

histgrid_sakaluk

```


### Seabrook

#### Seabrook total
```{r}

hist_seabrooktotal <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_total
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Total',
    y = 'Frequency',
    title = 'Sexual Scripts (Seabrook et al., 2016)'
  ) +
  theme_classic()

hist_seabrooktotal

```


#### Seabrook courtship
```{r}

hist_seabrookcourtship <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_courtship
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Courtship',
    y = 'Frequency',
    title = 'Courtship and Commitment (Seabrook et al., 2016)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_seabrookcourtship

```


#### Seabrook initiators
```{r}

hist_seabrookinitiators <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_initiators
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Initiators',
    y = 'Frequency',
    title = 'Men as initiators (Seabrook et al., 2016)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_seabrookinitiators

```


#### Seabrook appearance
```{r}

hist_seabrookappearance <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_appearance
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Appearance',
    y = 'Frequency',
    title = 'Women`s appearance (Seabrook et al., 2016)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_seabrookappearance

```


#### Seabrook double standards
```{r}

hist_seabrookdoublestandards <- 
  ggplot(data_heteroscales,
         aes(
           x = seabrook_doublestandards
         )) +
  geom_histogram(
    binwidth = .25,
    color = "black",
    fill = "grey"
  ) +
  scale_x_continuous(
    limits = c(1, 6),
    breaks = 1:6
  ) +
  labs(
    x = 'Double Standards',
    y = 'Frequency',
    title = 'Double Standards (Seabrook et al., 2016)'
  ) +
  theme_classic(
    base_size = 8
  )

hist_seabrookdoublestandards

```


#### Seabrook histogram grid
```{r}

histgrid_seabrook <- plot_grid(hist_seabrookcourtship, hist_seabrookinitiators, hist_seabrookappearance, hist_seabrookdoublestandards, nrow = 2)

histgrid_seabrook

```


### Krahé

#### Histogram grid items
```{r}

krahe_scale <- filter(data_heteroscales[76:115])


krahe_scale %>% 
    pivot_longer(
        cols = everything(),
        names_to = "item",
        values_to = "value"
    ) %>% 
  ggplot(.,
         aes(
           x = value
         )) +
  facet_wrap(
    ~ item,
    nrow = 5) +
  geom_histogram(
    binwidth = 1,
    color = "black",
    fill = "grey"
  ) +
  theme_classic(
    base_size = 9.5
  )

```


# Multivariate normality

## Ammsa total
```{r}

# Mardia's test
diagnostics_ammsa <- mvn(data_heteroscales[55:75],
                           mvnTest = 'mardia',
                           multivariateOutlierMethod = 'adj', # adjusted quantile method
                           showOutliers = T,
                           showNewData = T) # data without outliers

diagnostics_ammsa$multivariateNormality # mvn, skewness and kurtosis


# qqplot
ggplot(data_heteroscales,
        aes(
          sample = ammsa_total
        )) +
geom_qq(
  distribution = qnorm
) +
geom_qq_line(
  distribution = qnorm
) +
theme_classic()


# mahalanobis distances
cov_ammsa <- cov(data_heteroscales[55:75]) # cov matrix

colmeans_ammsa <- colMeans(data_heteroscales[55:75])

mahal_ammsa <- mahalanobis(data_heteroscales[55:75], center = colmeans_ammsa, cov = cov_ammsa)

mahal_p_ammsa <- pchisq(mahal_ammsa, df = ncol(data_heteroscales[55:75]), lower.tail = F)

ID_ammsa <- 1:nrow(data_heteroscales[55:75])

mahal_data_ammsa <- data.frame(ID_ammsa, mahal_ammsa, mahal_p_ammsa)

arrange(mahal_data_ammsa, by = desc(mahal_ammsa))


```


## Sakaluk total
```{r}

# Mardia's test
diagnostics_sakaluk <- mvn(data_heteroscales[1:32],
                           mvnTest = 'mardia',
                           multivariateOutlierMethod = 'adj', # adjusted quantile method
                           showOutliers = T,
                           showNewData = T) # data without outliers

diagnostics_sakaluk$multivariateNormality # mvn, skewness and kurtosis


# qqplot
ggplot(data_heteroscales,
        aes(
          sample = sakaluk_total
        )) +
geom_qq(
  distribution = qnorm
) +
geom_qq_line(
  distribution = qnorm
) +
theme_classic()


# mahalanobis distances
cov_sakaluktotal <- cov(data_heteroscales[1:32]) # cov matrix

colmeans_sakaluktotal <- colMeans(data_heteroscales[1:32])

mahal_sakaluktotal <- mahalanobis(data_heteroscales[1:32], center = colmeans_sakaluktotal, cov = cov_sakaluktotal)

mahal_p_sakaluktotal <- pchisq(mahal_sakaluktotal, df = ncol(data_heteroscales[1:32]), lower.tail = F)

ID_sakaluktotal <- 1:nrow(data_heteroscales[1:32])

mahal_data_sakaluktotal <- data.frame(ID_sakaluktotal, mahal_sakaluktotal, mahal_p_sakaluktotal)

arrange(mahal_data_sakaluktotal, by = desc(mahal_sakaluktotal)) # arrange descending


```


## Seabrook total
```{r}

# Mardia's test
diagnostics_seabrook <- mvn(data_heteroscales[33:54],
                           mvnTest = 'mardia',
                           multivariateOutlierMethod = 'adj', # adjusted quantile method
                           showOutliers = T,
                           showNewData = T) # data without outliers

diagnostics_seabrook$multivariateNormality # mvn, skewness and kurtosis


# qqplot
ggplot(data_heteroscales,
        aes(
          sample = seabrook_total
        )) +
geom_qq(
  distribution = qnorm
) +
geom_qq_line(
  distribution = qnorm
) +
theme_classic()


# mahalanobis distances
cov_seabrooktotal <- cov(data_heteroscales[33:54]) # cov matrix

colmeans_seabrooktotal <- colMeans(data_heteroscales[33:54])

mahal_seabrooktotal <- mahalanobis(data_heteroscales[33:54], center = colmeans_seabrooktotal, cov = cov_seabrooktotal)

mahal_p_seabrooktotal <- pchisq(mahal_seabrooktotal, df = ncol(data_heteroscales[33:54]), lower.tail = F)

ID_seabrooktotal <- 1:nrow(data_heteroscales[33:54])

mahal_data_seabrooktotal <- data.frame(ID_seabrooktotal, mahal_seabrooktotal, mahal_p_seabrooktotal)

arrange(mahal_data_seabrooktotal, by = desc(mahal_seabrooktotal))


```

##########################################################################################
