---
title: "Sexual Scripts Master Thesis Initial Cleaning & Demographics"
author: "Fanny Habacht"
date: "2023-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This code includes the initial dataset cleaning and demographics for my master thesis


# Packages
```{r}

packages <- c('dplyr', 'ggplot2', 'tidyr', 'readr', 'jtools', 'stringr')

lapply(packages, library, character.only = TRUE)

```


# Data preparation

## Loading data
```{r}

data <- read_csv('data_sexualscript_raw.csv') # load raw data

```


## Initial cleaning
```{r}

data_clean <- data %>%
  slice(-1, -2) %>% # remove first two rows (because they are not actual responses)
  filter(Progress == 100) %>% # removing unfinished surveys
  mutate(id = 1:nrow(.)) %>% # adding id column
  select(
    'id', 
    'Duration (in seconds)',
    'age',
    'gender',
    'sexuality',
    'monogamy',
    'nb_gender_attraction',
    starts_with('sexualstandards'), 
    starts_with('complexity'), 
    starts_with('sexdrive'), 
    starts_with('performanceandorgasm'), 
    starts_with('player'), 
    starts_with('emotionalsex'), 
    starts_with('courtship'), 
    starts_with('initiators'), 
    starts_with('appearance'), 
    starts_with('doublestandards'), 
    starts_with('ammsa'), 
    starts_with('arranged'), 
    starts_with('situation'), 
    starts_with('sex'), 
    starts_with('sexlocation'), 
    starts_with('contraception'), 
    starts_with('metbefore'), 
    starts_with('knownbefore'), 
    starts_with('substances'), 
    starts_with('drunkstoned'), 
    starts_with('consent'), 
    starts_with('afterfeeling'), 
    starts_with('outlook')
    ) %>%
  rename('duration' = 'Duration (in seconds)') # renaming duration column

```


## Character to numeric values
```{r}

sapply(data_clean, class) # check the class of each column


data_clean <- data_clean %>% mutate_if(is.character, as.numeric)


sapply(data_clean, class)


# remove accidental spaces from variable names

names(data_clean) <- str_replace_all(names(data_clean), c(" " = ""))


```


## Coalescing the gendered versions of the Krahé et al scale
```{r}

krahe_cols <- data_clean %>% # pick the relevant columns and define them as a separate data frame
  select(
    id,
    starts_with("arranged"),
    starts_with("situation"),
    starts_with("sex_"),
    starts_with("sexlocation"),
    starts_with("contraception"),
    starts_with("metbefore"),
    starts_with("knownbefore"),
    starts_with("substances"),
    starts_with("drunkstoned"),
    starts_with("consentboy"),
    starts_with("consentgirl"),
    starts_with("afterfeeling"),
    starts_with("outlook")
  ) %>% 
  pivot_longer( # combine all columns to one long column with names and one with the values
    cols      = colnames(select(., -id)),
    names_to  = "variable",
    values_to = "value",
    values_drop_na = TRUE 
  )


krahe_cols$variable <- gsub( # remove a space from the names
  pattern = " ", 
  replacement = "",
  x = krahe_cols$variable)


krahe_cols$variable <- gsub( # remove the _m from the names
  pattern = "_m", 
  replacement = "",
  x = krahe_cols$variable)


krahe_cols <- krahe_cols %>% # split the columns up again
  pivot_wider(
    id_cols     = "id",
    names_from  = "variable",
    values_from = "value"
  )


data_clean <- data_clean %>% # remove all columns from the original data set to avoid duplication
  select(
    -starts_with("arranged"),
    -starts_with("situation"),
    -starts_with("sex_"),
    -starts_with("sexlocation"),
    -starts_with("contraception"),
    -starts_with("metbefore"),
    -starts_with("knownbefore"),
    -starts_with("substances"),
    -starts_with("drunkstoned"),
    -starts_with("consentboy"),
    -starts_with("consentgirl"),
    -starts_with("afterfeeling"),
    -starts_with("outlook")
  ) %>% 
  left_join(krahe_cols, by = "id") # join the two data frames together after id (to match answer and person)

```


## Removing empty surveys
```{r}

nonbinary <- 3
notsaid <- 4
hetero <- 1
other <- 3


emptyrows <- data_clean %>% 
  filter(
    gender == nonbinary & sexuality != hetero | gender == notsaid & sexuality != hetero | gender == nonbinary & nb_gender_attraction == other | gender == notsaid & nb_gender_attraction == other)


data_clean <- data_clean %>% 
  anti_join(emptyrows)

```


# Saving cleaned dataset
```{r}

write.csv(data_clean, 'data_sexualscript_clean.csv', row.names = FALSE)

```


################################################################################


# Descriptive Analyses

## Demographics whole sample

### Age
```{r}

# function for calculating the statistical mode

mode <- function(codes){
  which.max(tabulate(codes))
} 


# summary of age

data_clean %>% 
  summarise(
    mean = mean(age, na.rm = TRUE), 
    sd = sd(age, na.rm = TRUE), 
    median = median(age, na.rm = TRUE),
    mode = mode(age),
    min = min(age, na.rm = TRUE), 
    max = max(age, na.rm = TRUE)
  )
```


```{r}

# summary of age, grouped by gender

data_clean %>% 
  group_by(gender) %>% 
  summarise(
    mean = mean(age, na.rm = TRUE), 
    sd = sd(age, na.rm = TRUE), 
    median = median(age, na.rm = TRUE),
    mode = mode(age),
    min = min(age, na.rm = TRUE), 
    max = max(age, na.rm = TRUE)
  )

```

#### Age frequency distributions
```{r}

# histogram of age distribution

hist_age <- 
  ggplot(data_clean,
       aes(
         x = age
       )) +
  geom_histogram(
    binwidth = 2, 
    fill = 'grey', 
    color = 'black'
  ) +
  labs(
    y = 'Frequency',
    x = 'Age',
    title = 'Age distribution'
  ) +
  scale_x_continuous(
    limits = c(18, max(data_clean$age)),
    breaks = seq(18, max(data_clean$age), 5)
  ) +
  scale_y_continuous(
    limits = c(0, max(data_clean$age)),
    breaks = seq(0, max(data_clean$age), 10)
  )+
  theme_classic()


hist_age

```


```{r}

# histrogram of age distribution by gender

genderlabels <- as_labeller(c ('1' = 'male', '2' = 'female', '3' = 'non-binary', '4' = 'prefer not to say'))


hist_agebygender <- 
  ggplot(data_clean,
       aes(
         x = age
       )) +
  facet_wrap(
    ~ gender,
    labeller = genderlabels,
    strip.position = 'bottom'
    ) +
  geom_histogram(
    binwidth = 2, 
    fill = 'grey', 
    color = 'black'
  ) +
  labs(
    y = 'Frequency',
    x = 'Age', 
    title = 'Age distribution by gender'
  ) +
  scale_x_continuous(
    limits = c(18, max(data_clean$age)),
    breaks = seq(18, max(data_clean$age), 5)
  ) +
  scale_y_continuous(
    limits = c(0, max(data_clean$age)),
    breaks = seq(0, max(data_clean$age), 20)
  )+
  theme_classic()


hist_agebygender

```


### Gender

1 = male
2 = female
3 = non-binary / third gender
4 = prefer not to say

```{r}

table(data_clean$gender) # absolute values

prop.table(table(data_clean$gender))*100 # percentages

```


### Sexuality

1 = heterosexual
2 = homosexual
3 = bisexual
4 = other
5 = prefer not to say

```{r}

table(data_clean$sexuality) # absolute values

prop.table(table(data_clean$sexuality))*100 # percentages

```


### Relationship Style

1 = monogamous
2 = consensually non-monogamous
3 = other

```{r}

table(data_clean$monogamy) # absolute values

prop.table(table(data_clean$monogamy))*100 # percentages

```


### Straight non-binary gender attraction

1 = male
2 = female

```{r}

table(data_clean$nb_gender_attraction) # absolute values

prop.table(table(data_clean$nb_gender_attraction))*100 # percentages

```


## Demographics hetero male/female
```{r}

hetero <- 1
nonbinary <- 3
notsaid <- 4


data_nothetero <- data_clean %>% 
  filter(sexuality != hetero)

data_onlyhetero <- data_clean %>% 
  anti_join(data_nothetero)

data_notmaleorfemale <- data_onlyhetero %>% 
  filter(gender == nonbinary | gender == notsaid)

data_onlyhetero_malefemale <- data_onlyhetero %>% 
  anti_join(data_notmaleorfemale)

```


### Age hetero male/female
```{r}

# summary of age hetero male/female

data_onlyhetero_malefemale %>% 
  summarise(
    mean = mean(age, na.rm = TRUE), 
    sd = sd(age, na.rm = TRUE), 
    median = median(age, na.rm = TRUE),
    mode = mode(age),
    min = min(age, na.rm = TRUE), 
    max = max(age, na.rm = TRUE)
  )

```


```{r}

# summary of age, grouped by gender (hetero male/female)

data_onlyhetero_malefemale %>% 
  group_by(gender) %>% 
  summarise(
    mean = mean(age, na.rm = TRUE), 
    sd = sd(age, na.rm = TRUE), 
    median = median(age, na.rm = TRUE),
    mode = mode(age),
    min = min(age, na.rm = TRUE), 
    max = max(age, na.rm = TRUE)
  )

```


#### Age frequency distributions hetero male/female
```{r}

# histogram of age distribution hetero male/female

hist_age_heteromalefemale <- 
  ggplot(data_onlyhetero_malefemale,
       aes(
         x = age
       )) +
  geom_histogram(
    binwidth = 2, 
    fill = 'grey', 
    color = 'black'
  ) +
  labs(
    y = 'Frequency',
    x = 'Age',
    title = 'Age distribution hetero male/female'
  ) +
  scale_x_continuous(
    limits = c(18, max(data_onlyhetero_malefemale$age)),
    breaks = seq(18, max(data_onlyhetero_malefemale$age), 5)
  ) +
  scale_y_continuous(
    limits = c(0, 50),
    breaks = seq(0, 50, 10)
  )+
  theme_classic()


hist_age_heteromalefemale

```


```{r}

# histrogram of age distribution by gender hetero male/female

genderlabels <- as_labeller( c('1' = 'male', '2' = 'female'))


hist_agebygender_heteromalefemale <- 
  ggplot(data_onlyhetero_malefemale,
       aes(
         x = age
       )) +
  facet_wrap(
    ~ gender,
    labeller = genderlabels,
    strip.position = 'bottom'
    ) +
  geom_histogram(
    binwidth = 2, 
    fill = 'grey', 
    color = 'black'
  ) +
  labs(
    y = 'Frequency',
    x = 'Age', 
    title = 'Age distribution by gender, hetero'
  ) +
  scale_x_continuous(
    limits = c(18, max(data_onlyhetero_malefemale$age)),
    breaks = seq(18, max(data_onlyhetero_malefemale$age), 10)
  ) +
  scale_y_continuous(
    limits = c(0, 50),
    breaks = seq(0, 50, 10)
  ) +
  theme_classic()


hist_agebygender_heteromalefemale

```


### Relationship style hetero male/female

1 = monogamous
2 = consensually non-monogamous
3 = other

```{r}

table(data_onlyhetero_malefemale$monogamy) # absolute values


prop.table(table(data_onlyhetero_malefemale$monogamy))*100 # percentages

```


################################################################################






